---
title: "Negative Incentive Framing Structures in Cognitively Demanding Tasks"
author: "Tshering Wangchuk and Franco Salinas Meza"
output: github_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = TRUE, warning = FALSE, message = FALSE)

library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(sf)
library(spdep)
library(spatialreg)
library(ggthemes)
```

```{r, results='hide'}
experiment<- read.csv('Data.csv')
data<-as.data.frame(experiment)
data_1 <- data %>% 
  filter(SL<31) %>% 
  select(-X,-X.1) 

##Given the low number of first years we could create two variables, one that it lower and upper classmen 

data_school_year<-data_1 %>% 
  mutate(school_status = ifelse(test = School_Year == 1|School_Year==2, yes = "Underclassmen",no = "Upperclassmen"))

##Given the low number of subjects in certain majors I grouped them into Stem and Social Science

data_major_category<-data_school_year%>% 
  mutate(Major_category = ifelse(Major=="Biology"|Major=="Computer Science"|Major=="Geology"|Major=="Neuroscience"|Major=="Statistics","STEM","Social Science")) %>% 
  mutate(accuracy_rate = Correct/12, share_questions_responded = (Passage.1+Passage.2)/12)

data_final <- data_major_category %>% 
  mutate(Gender = as.factor(Gender), 
         English_Native = as.factor(English_Native), 
         International = as.factor(International),
         Incentive_Structure = as.factor(Incentive_Structure),
         Workload = as.factor(Workload),
         school_status = as.factor(school_status), 
         Major_category = as.factor(Major_category))

data_correlation <- data_major_category %>% 
  mutate(Gender = ifelse(Gender== "Female" ,1,0),
         English_Native = ifelse(English_Native == "Yes",1, 0), 
         International = ifelse(International == "Yes",1,0),
         Incentive_Structure = ifelse(Incentive_Structure == "Positive",1,0),
         Workload = ifelse(Workload=="Large",1,0),
         school_status = ifelse(school_status == "Upperclassmen",1,0), 
         Major_category = ifelse(Major_category == "STEM",1,0))
```

```{r}

data_final %>% 
  ggplot(aes(x = Major_category,y = accuracy_rate), fill = blue)+
  geom_boxplot()+
  labs(title = "Figure 1: Accuracy Rate vs. Major Category",
       x=  "Major Category",
       y=  "Accuracy Rate")+
  theme_classic()
 
  

data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(school_status)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. School Year",
       x=  "School Year",
       y=  "Accuracy Rate")+
  theme_classic()


data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(English_Native)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Indicator of whether the Person is a Native Speaker",
       x=  "Is the subject a Native Speaker?",
       y=  "Accuracy Rate")+
  theme_classic()


data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(Incentive_Structure)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Incentive Structure",
       x=  "Incentive Structure",
       y=  "Accuracy Rate")+
  theme_classic()


data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(International)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Indicator if it's an international Student",
       x=  "Is the subject an International Student?",
       y=  "Accuracy Rate")+
  theme_classic()



data_final %>% 
  ggplot(aes(x = accuracy_rate, y = Guess))+
  geom_point()+
  labs(title = "Changes in accuracy rate with Number of Guesses")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = accuracy_rate, y = Hours_of_Sleep))+
  geom_point()+
  labs(title = "Changes in accuracy rate with Hours of Sleep")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = accuracy_rate, y = Number_of_Classes))+
  geom_point()+
  labs(title = "Changes in accuracy rate with Number of Classes")+
  theme_classic()

data_final %>% 
  ggplot(aes(y = accuracy_rate, x = Workload))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Workload",
       x=  "Is the subject experiencing a large or small workload?",
       y=  "Accuracy Rate")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = accuracy_rate, y = Gender))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Indicator for Gender",
       x=  "Is the subject male or female identifying?",
       y=  "Accuracy Rate")+
  theme_classic()

data_final %>% 
  ggplot(aes(y = share_questions_responded, x = Incentive_Structure))+
  geom_boxplot()+
  labs(title = "Figure 2: Share of Questions Responded vs. Incentive Structure",
       x=  "Is the subject male or female identifying?",
       y=  "Accuracy Rate")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = share_questions_responded))+
  geom_density(fill = "blue")+
  labs(title = "Figure 2: Distribution of Share of Questions Responded",
       y=  "Probability",
       x=  "Number of questions responded")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = Gender))+
  geom_bar()+
  labs(title = "Gender Representation",
       y=  "Count")+
  theme_classic()
  
data_final %>% 
  ggplot(aes(x = Major_category))+
  geom_bar()+
  labs(title = "Major Category Representation",
       y=  "Count")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = school_status))+
  geom_bar()+
  labs(title = "School Status Representation",
       y=  "Count")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = English_Native))+
  geom_bar()+
  labs(title = "Representation of Native English Speakers",
       y=  "Count")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = International))+
  geom_bar()+
  labs(title = "Representation of International Students",
       y=  "Count")+
  theme_classic()

data_final %>% 
  ggplot(aes(x = Incentive_Structure))+
  geom_bar()+
  labs(title = "Representation of both Incentive Structures",
       y=  "Count")+
  theme_classic()





data_correlation %>% 
  select(accuracy_rate, Gender, Number_of_Classes, share_questions_responded, English_Native,Incentive_Structure,Guess) %>% 
  cor()

```

Insights: 
  
  Model 1: Criteria(correlation larger than 0.1 or smaller than -0.1), I realized that variables with correlation that is lower than 0.3 or larger than -0.3 didn't have an important impact on the model.
    
    Gender 
    Number_of_Classes 
    share_questions_responded 
    English_Native 
    Incentive_Structure  
    Guess
## Understanding Factors that affect accuracy

Notes: 
  English native increased our p value by a lot 
  Gender increased by a little
  Number of classes incrased p value by a lot 
  
  
$$E[\text{Accuracy Rate}] = \beta_0+ \beta_1*\text{Incentive Structure}$$

$$E[\text{Accuracy Rate}] = \beta_0+ \beta_1*\text{Incentive Structure}+\beta_2*\text{Gender}+\beta_3*\text{Number of Classes}+\beta_4*\text{Share of Questions Responded}+\beta_5*\text{English Native}+\beta_6*\text{Number of Guesses}$$
  
```{r}


model1 <- lm(accuracy_rate~Incentive_Structure+Gender+Number_of_Classes+ share_questions_responded+English_Native+Guess ,data = data_final)

model_one_variable <- lm(accuracy_rate~Incentive_Structure,data = data_final)



# model1 <- lm(accuracy_rate~Incentive_Structure*Gender+Gender+school_status+English_Native+Number_of_Classes+Hours_of_Sleep+Workload+Major_category+share_questions_responded,data = data_final)
summary(model1)
summary(model_one_variable)


data_final %>% 
  mutate(predicted = predict(model1), residual = accuracy_rate - predicted) %>% 
  ggplot(aes(x=predicted, y=residual)) +
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  theme_classic()+
  labs(title= "Figure 2", subtitle = "Residual Plot",x = "Residuals", y = "Predictions")+
  scale_color_viridis_d(alpha = 1)

data_final %>% 
  mutate(predicted = predict(model_one_variable), residual = accuracy_rate - predicted) %>% 
  ggplot(aes(x=predicted, y=residual)) +
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  theme_classic()+
  labs(title= "Figure 2", subtitle = "Residual Plot",x = "Residuals", y = "Predictions")+
  scale_color_viridis_d(alpha = 1)

```


```{r}


library(huxtable)

huxreg(model1, model_one_variable, error_format = "[{p.value}]") %>% map_background_color(-1, -1, by_regex(
        "\\*" = "yellow"
      )) %>% 
      set_caption("Linear regressions of accuracy rates")

# tab <- huxreg(model1,
#               # Rename coefficients
#               coefs = c("Incentive Structure" = "Incentive_StructurePositive", "Male" = "GenderMale", "Upperclassmen" = "factor(school_status)Upperclassmen","English Native Speaker" = "English_NativeYes"),
#               # Add the desired summary statistics
#               statistics = c(N = "nobs", R2 = "r.squared", p-value = ""),
#               # Add a note
#               note = "Note. Important note about this table") %>% 
#   # Convert the huxtable table to flextable
#   as_flextable()
# 
# # Set a custom width to ensure it fits on the page
# tab %>% flextable::width(width = 1)
data_final %>% dim()

```


### Incentive Structure

```{r}
data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(Incentive_Structure)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Incentive Structure",
       x=  "Incentive Structure",
       y=  "Accuracy Rate")+
  theme_classic()
```

### School Year Status

```{r}
data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(school_status)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. School Year",
       x=  "School Year",
       y=  "Accuracy Rate")+
  theme_classic()
```

### English as a Native Language

```{r}
data_final %>% 
  ggplot(aes(y = accuracy_rate, x = factor(English_Native)))+
  geom_boxplot()+
  labs(title = "Figure 2: Accuracy Rate vs. Indicator of whether the Person is a Native Speaker",
       x=  "Is the subject a Native Speaker?",
       y=  "Accuracy Rate")+
  theme_classic()
```


## Understanding Factors that affect the share of questions responded: 

```{r}
data_correlation %>% 
  select(share_questions_responded,accuracy_rate, English_Native,International,Incentive_Structure,Workload, Gender) %>% 
  cor()
```

Accuracy rate
English_Native 
International 
Workload 
Incentive structure


$$E[\text{Share of Questions Responded}] = \beta_0+ \beta_1*\text{Accuracy Rate}+\beta_2*\text{Incentive Structure}+\beta_3*\text{English Native Speaker}+\beta_4*\text{International Student}+\beta_5*\text{Workload}$$


```{r}

model2<-lm(share_questions_responded~accuracy_rate+Incentive_Structure+English_Native+International+Workload,data = data_final)
summary(model2)


plot(resid(model2))

data_final %>% 
  mutate(predicted = predict(model2), residual = share_questions_responded - predicted) %>% 
  ggplot(aes(x=predicted, y=residual)) +
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  theme_classic()+
  labs(title= "Figure 2", subtitle = "Residual Plot",x = "Residuals", y = "Predictions")+
  scale_color_viridis_d(alpha = 1)

```





```{r}

huxreg(model2, error_format = "[{p.value}]") %>% map_background_color(-1, -1, by_regex(
        "\\*" = "yellow"
      )) %>% 
      set_caption("Linear regressions of Share of questions Responded")
```



```{r}
data_final %>% 
  ggplot(aes(y = share_questions_responded, x = Incentive_Structure))+
  geom_boxplot()+
  labs(title = "Figure 2: Share of Questions Responded vs. Incentive Structure",
       x=  "Is the subject male or female identifying?",
       y=  "Accuracy Rate")+
  theme_classic()

```

```{r}
data_final %>% 
  ggplot(aes(y = share_questions_responded, x = Number_of_Classes))+
  geom_boxplot()+
  labs(title = "Figure 2: Share of Questions Responded vs. Incentive Structure",
       x=  "Is the subject male or female identifying?",
       y=  "Accuracy Rate")+
  theme_classic()

```

```{r}
data_final %>% 
  ggplot(aes(y = share_questions_responded, x = Hours_of_Sleep))+
  geom_boxplot()+
  labs(title = "Figure 2: Share of Questions Responded vs. Incentive Structure",
       x=  "Is the subject male or female identifying?",
       y=  "Accuracy Rate")+
  theme_classic()

```

```{r}
data_final %>% 
  ggplot(aes(y = share_questions_responded, x = Workload))+
  geom_boxplot()+
  labs(title = "Figure 2: Share of Questions Responded vs. Incentive Structure",
       x=  "Is the subject male or female identifying?",
       y=  "Accuracy Rate")+
  theme_classic()

```

